---
title: "Multi-Campaign Analysis"
output: pdf_document
---


```{r include=TRUE, echo=FALSE,warning=FALSE}
library(ggplot2)
library(gridExtra)
source("~/Documents/ETH/ASL/ASL_Middleware/analysis/R/External.R")
source("~/Documents/ETH/Thesis/1plusX/Data/thesis/R/ManageCampaignsLib.R")

imageLocation = "~/Documents/ETH/Thesis/1plusX/Data/thesis/1plusx/Results/Images/CampaignData/"
impressionScale = 2.23
ctrScale = 1.57


```

```{r include=TRUE, echo=FALSE, warning=FALSE}
library(scales)
path = "~/Documents/ETH/Thesis/1plusX/Data/RawData/Campaigns/5/Processed/all_impressions_agg.csv"
data <- read.csv(file=path, header=TRUE, sep=",")
data$Timestamp = data$Timestamp / 1000
data$Timestamp = as.POSIXct(data$Timestamp, origin="1970-01-01")
#startDate <- as.Date("15-08-2018", "%d-%m-%Y")data$Timestamp
startDate <- as.POSIXct(strptime("2018-08-15 00:00:00", "%Y-%m-%d %H:%M:%S"))
endDate <- as.POSIXct(strptime("2018-08-21 00:00:00", "%Y-%m-%d %H:%M:%S"))
data = subset(data, Timestamp >= startDate & Timestamp < endDate)
data$Impressions = data$Impressions * impressionScale
data = renameCampaignIds(data)

g1 = ggplot(data, aes(fill=factor(CampaignId), y=Impressions, x=Timestamp)) +
  geom_bar( stat="identity") +
  theme_bw() +
  ylab("Impression Count (Scaled)") +
  scale_fill_discrete(name="Campaigns") +
  scale_y_continuous(labels=formatterM()) + 
  scale_x_datetime(breaks = date_breaks("1 day"), labels = date_format("%a")) +
  theme(axis.text.x=element_text(angle = 45, hjust = 1, size=7),
        legend.justification=c(1,0), 
        legend.title=element_text(size=12), 
        legend.text=element_text(size=8), 
        legend.key.size = unit(1,"line"),
        axis.title.x=element_blank(),
        plot.title = element_text(size = 14, face = "bold"), 
        axis.title.y = element_text(size=10)) 
  ggtitle("Impressions per Campaign")

ggsave(paste(imageLocation, "ImpressionsPerCampaign.png", sep=""), plot=g1, width = 20, height = 11, units = "cm")
g1

```


```{r include=TRUE, echo=FALSE, warning=FALSE}
library(scales)
path = "~/Documents/ETH/Thesis/1plusX/Data/RawData/Campaigns/5/Processed/all_impressions_agg.csv"
data <- read.csv(file=path, header=TRUE, sep=",")
data$Timestamp = data$Timestamp / 1000
data$Timestamp = as.POSIXct(data$Timestamp, origin="1970-01-01")
startDate <- as.POSIXct(strptime("2018-08-15 00:00:00", "%Y-%m-%d %H:%M:%S"))
endDate <- as.POSIXct(strptime("2018-08-21 00:00:00", "%Y-%m-%d %H:%M:%S"))
data = subset(data, Timestamp >= startDate & Timestamp < endDate)
data$Impressions = data$Impressions * impressionScale
data$CTR = data$CTR * ctrScale
data = renameCampaignIds(data)

g2 = ggplot(data, aes(color=factor(CampaignId), y=CTR, x=Timestamp)) +
  #geom_bar( stat="identity") +
  #stat_smooth(aes(color=factor(CampaignId), y=CTR, x=Timestamp), method = "lm", formula = y ~ poly(x, 20), se = FALSE, size=2) +
  geom_line()+
  ylab("CTR (Scaled)") +
  scale_color_discrete(name="Campaign") +
  scale_y_continuous(labels=percent)+
  theme_bw() +
  scale_x_datetime(breaks = date_breaks("1 day"), labels = date_format("%a")) +
  theme(axis.text.x=element_text(angle = 45, hjust = 1, size=7),
        legend.justification=c(1,0), 
        legend.title=element_text(size=12), 
        legend.text=element_text(size=8), 
        legend.key.size = unit(1,"line"),
         axis.title.x=element_blank(),
        plot.title = element_text(size = 14, face = "bold"), 
        axis.title.y = element_text(size=10)) 
#+  ggtitle("CTR per Campaign")

ggsave(paste(imageLocation, "CTRPerCampaign.png", sep=""), plot=g2, width = 20, height = 11, units = "cm")
g2

p = plotGroupNoTitle(g1, g2, 9) 
ggsave(paste(imageLocation, "ImpressionsAndCTRPerCampaign.png", sep=""), plot=p, width = 18, height = 10, units = "cm")

```



```{r include=TRUE, echo=FALSE, warning=FALSE}

columnNames = c("CampaignId", "Method", "RecommendationPart", "CTR", "Clicks", "Impressions", "FullFNR", "FullTPR", "BaseCTR", "Ratio")
all = data.frame(matrix(vector(), 0, length(columnNames), dimnames=list(c(), columnNames)), stringsAsFactors=F)
campaignIds = c(866128, 856805, 847460, 858140, 865041)
alphas = c(0.1, 0.01, 0.1, 0.1, 0.1)
index = 1
for (campaignId in campaignIds)
{
  random = getCampaignMetrics(files =  c("Random_Metrics"),  campaignId = campaignId, baseCTR=0, method="Random", alpha = 0)
  data = getCampaignMetrics(files = c("LinUCB_Disjoint_Metrics"), campaignId = campaignId, baseCTR=random[1, "CTR"], method="LinUCB_Disjoint", alpha = alphas[index]) 
  
  data$RecommendationPartGainsRatio = data$FullTPR * 100 / data$RecommendationPart
  all = rbind(all, data) 
  index = index + 1  
}

ratioData <- summarySE2(all, measurevar=c("Ratio"), groupvars=c("CampaignId"))
fprData <- summarySE2(all, measurevar=c("RecommendationPartGainsRatio"), groupvars=c("CampaignId"))

ratioData$CampaignId = factor(ratioData$CampaignId)
fprData$CampaignId = factor(fprData$CampaignId)
g1 = getBarPlotCampaigns(ratioData, yLabel = "Cumulative CTR Ratio", title="")
g2 = getBarPlotCampaigns(fprData, yLabel = "TPR Ratio", title="")

width = 8
g = plotGroupNoLegend(g1, g2, "CTR and TPR Ratio for Campaigns from Multi-Campaign List", width) 
ggsave(paste(imageLocation, "CTRRationPerCampaign.png", sep=""), plot=g, width = width * 2, height = 11, units = "cm")
g
```

```{r include=TRUE, echo=FALSE, warning=FALSE}

columnNames = c("CampaignId", "Timestamp", "BatchCTR")
all = data.frame(matrix(vector(), 0, length(columnNames), dimnames=list(c(), columnNames)), stringsAsFactors=F)
campaignIds = c(866128, 856805, 847460, 858140, 865041)
alphas = c(0.1, 0.01, 0.1, 0.1, 0.1)
index = 1
files = c("LinUCB_Disjoint_Metrics")
for (campaignId in campaignIds)
{
  path = paste("~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/", campaignId, "/", sep="")
  data = prepData(files, path)
  data = subset(data, Impressions > 1000 & RecommendationPart == 0.2 & Alpha == alphas[index] )
  data$CampaignId = campaignId
  all = rbind(all, data[columnNames]) 
}

all$Timestamp = as.numeric(all$Timestamp) / 1000
all$Timestamp = as.POSIXct(all$Timestamp, origin="1970-01-01")
g = ggplot(all, aes(color=factor(CampaignId), y=BatchCTR, x=Timestamp)) +
  geom_line()+
  scale_color_discrete(name="CampaignId") +
  theme_bw() +
  scale_x_datetime(breaks = date_breaks("1 day"), labels = date_format("%b %e")) +
  theme(axis.text.x=element_text(angle = 45, hjust = 1, size=7),
        legend.justification=c(1,0), 
        legend.title=element_text(size=12), 
        legend.text=element_text(size=8), 
        legend.key.size = unit(1,"line"),
        plot.title = element_text(size = 14, face = "bold"), 
        axis.title.y = element_text(size=10)) +
  ggtitle("Batch CTR per Campaign")

ggsave(paste(imageLocation, "BatchCTRPerCampaign.png", sep=""), plot=g, width = 16, height = 11, units = "cm")
g
```
For each campaign there are users that observed only that campaign and ones that are shared beween multiple campaigns. 
Below is the breakdown of the percentage of users per campaign that have seen only that campaign.


```{r include=TRUE, echo=FALSE, warning=FALSE}
library(scales)
path = "~/Documents/ETH/Thesis/1plusX/Data/RawData/Campaigns/5/Processed/MultiCampaignStats.csv"
data <- read.csv(file=path, header=TRUE, sep=",")
data$PercentUniqueUsers = (data$NonJoinedUserCount / data$TotalDistinctUserCount) * 100
data$Date = as.POSIXct(as.Date(data$Date))
g = ggplot(data, aes(color=factor(CampaignId), y=PercentUniqueUsers, x=Date)) +
  #geom_bar( stat="identity") +
  #stat_smooth( aes(color=factor(CampaignId), y=PercentUniqueUsers, x=Date), method = "lm", formula = y ~ poly(x, 20), se = FALSE, size=2) +
  geom_line()+
  scale_color_discrete(name="CampaignId") +
  theme_bw() +
  ylab("User Percent") +
  scale_y_continuous(labels=formatterPercent()) + 
  scale_x_datetime(breaks = date_breaks("1 day"), labels = date_format("%b %e")) +
  theme(axis.text.x=element_text(angle = 45, hjust = 1, size=7),
        legend.justification=c(1,0), 
        legend.title=element_text(size=12), 
        legend.text=element_text(size=8), 
        legend.key.size = unit(1,"line"),
        plot.title = element_text(size = 14, face = "bold"), 
        axis.title.y = element_text(size=10)) +
  ggtitle("Percentage of Users Uniquely Seen by Campaign per Day")

ggsave(paste(imageLocation, "UniqueUsersPerCampaign.png", sep=""), plot=g, width = 20, height = 11, units = "cm")
g
```

A breakdown of users per how many campaigns per day have they seen.
Majority of the users have seen a single unique campaign per day.


```{r include=TRUE, echo=FALSE, warning=FALSE}
library(scales)
path = "~/Documents/ETH/Thesis/1plusX/Data/RawData/Campaigns/5/Processed/MultiCampaignUserStats.csv"
data <- read.csv(file=path, header=TRUE, sep=",")
data$Date = as.POSIXct(as.Date(data$Date))
data$Date = as.POSIXct(data$Date, origin="1970-01-01")
startDate <- as.POSIXct(strptime("2018-08-15 00:00:00", "%Y-%m-%d %H:%M:%S"))
endDate <- as.POSIXct(strptime("2018-08-21 00:00:00", "%Y-%m-%d %H:%M:%S"))
data = subset(data, Date >= startDate & Date < endDate)

groupedData <- summarySE(data, 
            measurevar=c("UserCount"),
            groupvars=c("CampaignCount"))


g1 = ggplot(data, aes(fill=factor(CampaignCount), y=UserCount, x=Date)) +
   geom_bar(position = "fill",stat = "identity") +
  scale_y_continuous(labels=percent)+
  theme_bw() +
  ylab("User % of Click Users") +
#  scale_y_continuous(labels=formatterK()) + 
  scale_fill_discrete(name="# Observed\nCampaigns") +
  scale_x_datetime(breaks = date_breaks("1 day"), labels = date_format("%a")) +
  theme(axis.text.x=element_text(angle = 45, hjust = 1, size=7),
        legend.title=element_text(size=12), 
        legend.text=element_text(size=8), 
        legend.key.size = unit(1,"line"),
        legend.position = "bottom",
        axis.title.x=element_blank(),
        plot.title = element_text(size = 14, face = "bold"), 
        axis.title.y = element_text(size=10)) 
#+ ggtitle("% Users grouped by # Observed Campaigns")

ggsave(paste(imageLocation, "UsersGroupsPerCampaign.png", sep=""), plot=g1, width = 10, height = 10, units = "cm")
g1

```


The question to answer with the following two graphicsis: Can we identify "click users"?  


```{r include=TRUE, echo=FALSE, warning=FALSE}
library(scales)
path = "~/Documents/ETH/Thesis/1plusX/Data/RawData/Campaigns/5/Processed/MultiCampaignClickStats.csv"
data <- read.csv(file=path, header=TRUE, sep=",")
data$Date = as.POSIXct(as.Date(data$Date))

dailyTotal <- aggregate(data$UserCount, by=list(Category=data$Date), FUN=sum)
data$UserPercent = 0

for (d in unique(data$Date)) 
{
  data[data$Date ==d, ]$UserPercent = data[data$Date ==d, ]$UserCount / dailyTotal[dailyTotal$Category == d, ]$x
}
#data = subset(data, CampaignCount != 1)
summary <- summarySE2(data, measurevar=c("UserPercent"), groupvars=c("CampaignCount", "ClickedCampaignsCount"))
summary$ClickedCampaignsCount
summary$Factor = factor(paste(summary$ClickedCampaignsCount, "/", summary$CampaignCount, sep=""))

g2 = ggplot(summary, aes(x=Factor, y=mean, fill=Factor)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
    ylab("User Percent") + 
    xlab("#Clicked/#Seen Campaigns") + 
   #ggtitle("Daily Click Users: (# Clicked Campaigns) / (# Seen Campaigns)") +
    theme_bw() +
    scale_fill_hue("#Clicked / #Seen\nCampaigns")+ 
   scale_y_continuous(labels = percent)+
    theme(#axis.text.x=element_text(angle = 45, hjust = 1, size=7),
        legend.title=element_text(size=12), 
        legend.text=element_text(size=8), 
        legend.key.size = unit(1,"line"),
        legend.position = "none",
         #axis.title.x=element_blank(),
        plot.title = element_text(size = 14, face = "bold"), 
        axis.title.y = element_text(size=10))  
  
ggsave(paste(imageLocation, "ClickersPerCampaignSeen.png", sep=""), plot=g2, width = 10, height = 10, units = "cm")
g2

```


```{r include=TRUE, echo=FALSE, warning=FALSE}
library(scales)
path = "~/Documents/ETH/Thesis/1plusX/Data/RawData/Campaigns/5/Processed/MultiCampaignUserClickStats.csv"
data <- read.csv(file=path, header=TRUE, sep=",")
data$Date = as.POSIXct(as.Date(data$Date))
data <- read.csv(file=path, header=TRUE, sep=",")
data$Date = as.POSIXct(as.Date(data$Date))
data$Date = as.POSIXct(data$Date, origin="1970-01-01")
startDate <- as.POSIXct(strptime("2018-08-15 00:00:00", "%Y-%m-%d %H:%M:%S"))
endDate <- as.POSIXct(strptime("2018-08-21 00:00:00", "%Y-%m-%d %H:%M:%S"))
data = subset(data, Date >= startDate & Date < endDate)

mean(subset(data, CampaignCount == 1)$PercentFromTotalClickUserCount)
g = ggplot(data, aes(fill=factor(CampaignCount), y=ClickUserCount, x=Date)) +
  geom_bar(position = "fill",stat = "identity") +
  theme_bw() +
  ylab("User Percent") +
  scale_y_continuous(labels=percent)+
  scale_fill_discrete(name="# Clicked\nCampaigns") +
  scale_x_datetime(breaks = date_breaks("1 day"), labels = date_format("%a")) +
  theme(axis.text.x=element_text(angle = 45, hjust = 1, size=7),
        legend.justification=c(1,0), 
        legend.title=element_text(size=12), 
        legend.text=element_text(size=8), 
        legend.key.size = unit(1,"line"),
        axis.title.x=element_blank(),
        plot.title = element_text(size = 14, face = "bold"), 
        axis.title.y = element_text(size=10)) 
#+ ggtitle("# Click Users grouped by # Campaigns they have clicked on")


ggsave(paste(imageLocation, "ClickersPerCampaignCount.png", sep=""), plot=g, width = 20, height = 11, units = "cm")
g

```

```{r include=TRUE, echo=FALSE, warning=FALSE}
columnNames = c("CampaignId", "Method", "RecommendationPart", "CTR", "Clicks", "Impressions", "FullFNR", "FullTPR", "BaseCTR", "Ratio", "Timestamp")
all = data.frame(matrix(vector(), 0, length(columnNames), dimnames=list(c(), columnNames)), stringsAsFactors=F)
campaignIds = c(866128, 856805, 847460, 858140, 865041)
for (campaignId in campaignIds)
{
  random = getCampaignMetrics(files =  c("Random_Metrics"),  campaignId = campaignId, baseCTR=0, method="Random")
  data = getCampaignMetrics(files = c("LinUCB_Disjoint_Metrics"), campaignId = campaignId, baseCTR=random[1, "CTR"], method="LinUCB_Disjoint", alpha = 0.1) 
  data$RecommendationPartGainsRatio = data$FullTPR * 100 / data$RecommendationPart
  all = rbind(all, data) 
}
all$Timestamp = as.numeric(all$Timestamp) / 1000
all$Date = (as.integer(all$Timestamp / (24*3600))) * (24*3600)
all$Date = as.POSIXct(all$Date, origin="1970-01-01")

clicks = sum(all$Clicks)
impressions = sum(all$Impressions)
CTR = clicks/ impressions
# 0.004783994 - for the first 6 days (till 20th)
# 0.003313168 - for the entire duration
cat (paste("Achieved CTR when training each one of the campaigns separately: ", CTR, sep=""))

files =  c("Random_Metrics", "LinUCB_Disjoint_Metrics") # , "LinUCB_Disjoint_Multi_Metrics"
path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/5/"
data = prepData(files, path)

data$Factor = factor(paste(data$Method, " A:", data$Alpha, sep=""))
#data$Percent = data$BatchCTR * 100
getCTRPlot(data, c(0,0.6)) + 
  geom_hline(yintercept = CTR * 100) +
  ggtitle("Learn Combined Campaign Data (Hindsight CTR - Learn Each Campaign Individually)")+
  theme(plot.title = element_text(size=15,hjust = 0.5))

```

