---
title: "Algorithm comparison"
author: "Ana Dimitrova"
output: pdf_document

---
 

```{r setup, include=TRUE, echo=FALSE}
library(ggplot2)
library(scales)
library(gridExtra)

source("~/Documents/ETH/ASL/ASL_Middleware/analysis/R/External.R")
imageLocation = "~/Documents/ETH/Thesis/1plusX/Data/thesis/1plusx/Results/Images/Single-Campaign/"
path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/Simulation/Results/"
plot_results <- function(algorith_name="Random") {
  
  data <- read.csv(file=paste0(path, paste0(algorith_name, ".csv")), header=TRUE, sep=",")
  data$Percent = data$Clicks / data$Impressions * 100
  data$Factor = paste(data$Method, data$Alpha, sep=" ")

  ggplot(data, aes(x=Impressions, y=Percent, colour=Factor)) + 
  geom_line() + xlab("Impressions") + ylab("% of Clicks") +
  expand_limits(y=c(4,7.5), x=c(0, 75000)) + theme_bw() + ggtitle(algorith_name)
}
  
```

Simulation using real embeddings from 1plusX with simulated clicks.
Used randomly generated theta for evaluating the click value.
The click result = user.dot(theta) + error.
Clearly linear correlation and therefore very good results with linear regression. 

```{r linucb-hybrid, include=TRUE, echo=FALSE}
algorith_name="Simulation_Results"
data <- read.csv(file=paste0(path, paste0(algorith_name, ".csv")), header=TRUE, sep=",")
data$Percent = data$X7 / data$X100 * 100
data$Factor = paste(data$SRandom, data$X0.00, sep=" ")

ggplot(data, aes(x=X100, y=Percent, colour=Factor)) + 
geom_line() + xlab("Impressions") + ylab("% of Clicks") +
expand_limits(y=c(0,100), x=c(0, 20000)) + theme_bw()  + ggtitle("Linear - CTR: 5% - No added randomization")
  
```
Using a more complicated click function =sigma( A.dot(user^2) + B(user) + C ) + error
However clearly this is still not very sophisticated function. Still very good results with using a simple regression model.
CTR - 5% 
Using SEGreedy with a different exploration percentage. Interestingly the larger exploration the worse results. 
```{r gpprank, include=TRUE, echo=FALSE}
algorith_name="Simulation_Results_Poly"
data <- read.csv(file=paste0(path, paste0(algorith_name, ".csv")), header=TRUE, sep=",")
data$Percent = data$X4 / data$X100 * 100
data$Factor = paste(data$SRandom, data$X0.00, sep=" ")

ggplot(data, aes(x=X100, y=Percent, colour=Factor)) + 
geom_line() + xlab("Impressions") + ylab("% of Clicks") +
expand_limits(y=c(0,100), x=c(0, 10000)) + theme_bw() + ggtitle("Polynomial + Sigmoid - CTR: 5% - No added randomization")
```
Similarly to above, but adding more substantial error. 
The error takes random 5% of the generated clicks and flips them ot no click and takes same amount of no-clicks and makes them clicks. 

Also reducing the size of the CTR so that we can see more real world CTR for ads. 
The number of impressions this is equal to 70% of the total clicks. If an user is selected then he could not be chosen again, so we know that past 100% of clicks the ctr would fall drastically and no need to test that.

Clearly the lower CTR affects learning rate and results in a lower CTR, however it still performs quite well. 

```{r Poly_Sigmoid, include=TRUE, echo=FALSE , fig.width = 4}
algorith_name<-"Poly_Sigmoid"
data <- read.csv(file=paste0(path, paste0(algorith_name, ".csv")), header=TRUE, sep=",")

data$Percent = data$ClickCount / data$Impressions * 100
data$Algorithm = paste(data$AlgoName)
data_non_random = data[data$AlgoName != "SRandom",]

groupedData <- summarySE(data_non_random, 
            measurevar=c("Percent"),
            groupvars=c("Impressions", "AlgoName", "Alpha", "OverallCTR", "Algorithm"))

p1 = ggplot(groupedData[groupedData$OverallCTR ==0.005,], aes(Impressions, y=mean, colour=Algorithm)) + 
  geom_ribbon(aes(ymin=mean-se, ymax=mean+se, linetype=NA, fill=Algorithm), alpha=.3) +
  expand_limits(y=c(0,100)) +
  geom_line() + xlab("Impressions") + ylab("% of Clicks") +
 theme_bw() + ggtitle("CTR: 0.5%")+ theme(legend.position="bottom",legend.direction="horizontal")

p2 = ggplot(groupedData[groupedData$OverallCTR ==0.01,], aes(Impressions, y=mean, colour=Algorithm)) + 
  geom_ribbon(aes(ymin=mean-se, ymax=mean+se, linetype=NA, fill=Algorithm), alpha=.3) +
  expand_limits(y=c(0,100)) +
  geom_line() + xlab("Impressions") + ylab("% of Clicks") +
 theme_bw() + ggtitle("CTR: 1%") 

p3 = ggplot(groupedData[groupedData$OverallCTR ==0.02,], aes(Impressions, y=mean, colour=Algorithm)) + 
  geom_ribbon(aes(ymin=mean-se, ymax=mean+se, linetype=NA, fill=Algorithm), alpha=.3) +
  expand_limits(y=c(0,100)) +
  geom_line() + xlab("Impressions") + ylab("% of Clicks") +
 theme_bw() + ggtitle("CTR: 2%")  + theme(legend.position="bottom",legend.direction="horizontal")

g_legend2<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
  }

mylegend <- g_legend2(p1)
grid.arrange(arrangeGrob(p1 + theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         p3 + theme(legend.position="none"),
                        nrow=1, ncol=3, widths=unit(c(6.5,6.5,6.5), "cm"), heights=unit(6.5, "cm")),
                   mylegend, nrow=2, widths=unit(6.5*3, "cm"), heights=unit(c(9, 1), "cm"))


#ggsave(paste(imageLocation,"Experiment4Write.png", sep=""), plot=p4, width = 20, height = 10, units = "cm")

```

Exploring using an iterative algorithm instead of learning from scratch with linear regression. 
Using SGDRegressor. The results are worse, but not that drastically. Could be used in a long term evaluation for a large amount of data.
```{r Poly_Sigmoid_CGD, include=TRUE, echo=FALSE, fig.width = 4 }
algorith_name<-"Poly_Sigmoid_SGD"
data <- read.csv(file=paste0(path, paste0(algorith_name, ".csv")), header=TRUE, sep=",")

data$Percent = data$ClickCount / data$Impressions * 100
data$Algorithm = paste(data$AlgoName)
data_non_random = data[data$AlgoName != "SRandom",]

groupedData <- summarySE(data_non_random, 
            measurevar=c("Percent"),
            groupvars=c("Impressions", "AlgoName", "Alpha", "OverallCTR", "Algorithm"))

p1 = ggplot(groupedData[groupedData$OverallCTR ==0.005,], aes(Impressions, y=mean, colour=Algorithm)) + 
  geom_ribbon(aes(ymin=mean-se, ymax=mean+se, linetype=NA, fill=Algorithm), alpha=.3) +
  expand_limits(y=c(0,100)) +
  geom_line() + xlab("Impressions") + ylab("% of Clicks") +
 theme_bw() + ggtitle("CTR: 0.5%")+ theme(legend.position="bottom",legend.direction="horizontal")


p2 = ggplot(groupedData[groupedData$OverallCTR ==0.01,], aes(Impressions, y=mean, colour=Algorithm)) + 
  geom_ribbon(aes(ymin=mean-se, ymax=mean+se, linetype=NA, fill=Algorithm), alpha=.3) +
  expand_limits(y=c(0,100)) +
  geom_line() + xlab("Impressions") + ylab("% of Clicks") +
 theme_bw() + ggtitle("CTR: 1%") 

p3 = ggplot(groupedData[groupedData$OverallCTR ==0.02,], aes(Impressions, y=mean, colour=Algorithm)) + 
  geom_ribbon(aes(ymin=mean-se, ymax=mean+se, linetype=NA, fill=Algorithm), alpha=.3) +
  expand_limits(y=c(0,100)) +
  geom_line() + xlab("Impressions") + ylab("% of Clicks") +
 theme_bw() + ggtitle("CTR: 2%")  + theme(legend.position="bottom",legend.direction="horizontal")

g_legend2<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
  }


mylegend <- g_legend2(p1)
grid.arrange(arrangeGrob(p1 + theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         p3 + theme(legend.position="none"),
                        nrow=1, ncol=3, widths=unit(c(6.5,6.5,6.5), "cm"), heights=unit(6.5, "cm")),
                   mylegend, nrow=2, widths=unit(6.5*3, "cm"), heights=unit(c(9, 1), "cm"))


#ggsave(paste(imageLocation,"Experiment4Write.png", sep=""), plot=p4, width = 20, height = 10, units = "cm")

```


```{r Poly_Sigmoid_alphas, include=TRUE, echo=FALSE}
algorith_name<-"Poly_Sigmoid_Alpha"
data <- read.csv(file=paste0(path, paste0(algorith_name, ".csv")), header=TRUE, sep=",")

data$Percent = data$ClickCount / data$Impressions * 100
data$Algorithm = paste(data$Alpha)
data_non_random = data[data$AlgoName != "SRandom",]

groupedData <- summarySE(data_non_random, 
            measurevar=c("Percent"),
            groupvars=c("Impressions", "AlgoName", "Alpha", "OverallCTR", "Algorithm"))

p1 = ggplot(groupedData[groupedData$OverallCTR ==0.005,], aes(Impressions, y=mean, colour=Algorithm)) + 
  geom_ribbon(aes(ymin=mean-se, ymax=mean+se, linetype=NA, fill=Algorithm), alpha=.3) +
  expand_limits(y=c(0,100)) +
  geom_line() + xlab("Impressions") + ylab("% of Clicks") +
 theme_bw() + ggtitle("CTR: 0.5%")+ theme(legend.position="bottom",legend.direction="horizontal")


p2 = ggplot(groupedData[groupedData$OverallCTR ==0.02 & groupedData$Impressions < 15000,], aes(Impressions, y=mean, colour=Algorithm)) + 
  geom_ribbon(aes(ymin=mean-se, ymax=mean+se, linetype=NA, fill=Algorithm), alpha=.3) +
  expand_limits(y=c(0,100), x=c(0, 15000)) +
  geom_line() + xlab("Impressions") + ylab("% of Clicks") +
 theme_bw() + ggtitle("CTR: 2%")  + theme(legend.position="bottom",legend.direction="horizontal")

g_legend2<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
  }


mylegend <- g_legend2(p1)
grid.arrange(arrangeGrob(p1 + theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                        nrow=1, ncol=2, widths=unit(c(9, 9), "cm"), heights=unit(9, "cm")),
                   mylegend, nrow=2, widths=unit(18, "cm"), heights=unit(c(9, 1), "cm"))


#ggsave(paste(imageLocation,"Experiment4Write.png", sep=""), plot=p4, width = 20, height = 10, units = "cm")

```


```{r Poly_Sigmoid_alphas, include=TRUE, echo=FALSE}
algorith_name<-"LinUCB_Disjoint"

data <- read.csv("~/Documents/ETH/Thesis/1plusX/Data/thesis/1plusx/Results/837817/Simulated/LinUCB_Disjoint.csv", header=TRUE, sep=",")

data$Percent = data$Click / data$Impressions * 100
data$Factor = paste(data$RecommendationPart * 100 , "%", sep = )
data$Factor = factor(data$Factor, levels = unique(data$Factor[order(data$RecommendationPart)]))

#reorder(x, sort(as.numeric(x)))

groupedData <- summarySE(data, 
            measurevar=c("Percent"),
            groupvars=c("TotalImpressions", "Factor"))

#data = subset(data, SimulationId == 4)
#getCTRPlot(groupedData, c(0,0.3)) + 
#  ggtitle("CTR Comparison")

ggplot(groupedData, aes(TotalImpressions, y=mean, colour=Factor)) + 
  geom_ribbon(aes(ymin=mean-se, ymax=mean+se, linetype=NA, fill=Factor), alpha=.3, show_guide=FALSE) +
  expand_limits(y=c(0,30), x=c(0, 15000)) +
  geom_line() + 
  xlab("Impressions") + 
  ylab("CTR") +
  scale_x_continuous(labels=formatterM()) + 
  scale_y_continuous(labels=formatterPercent()) +
  labs(colour="Rec.Size:") + 
  theme_bw() +
  ggtitle("Recommendation Size Effects")  + 
  theme(legend.position="bottom",legend.direction="horizontal")

#ggsave(paste(imageLocation,"Experiment4Write.png", sep=""), plot=p4, width = 20, height = 10, units = "cm")

```

```{r Best, include=TRUE, echo=FALSE, warning=FALSE}
source("~/Documents/ETH/ASL/ASL_Middleware/analysis/R/External.R")

# 597165 - 0.001
# 722100 - 0.01, 0.001
# 809153 - to rerun entirely
columnNames = c("CampaignId", "Method", "RecommendationPart", "CTR", "Clicks", "Impressions", "FullFNR", "FullTPR", "BaseCTR", "Ratio")
all = data.frame(matrix(vector(), 0, length(columnNames), dimnames=list(c(), columnNames)), stringsAsFactors=F)
campaignIds = c(837817)
files =  c("Random")
for (campaignId in campaignIds)
{
  random = getCampaignMetricsSimulated(files =  c("Random"),  campaignId = campaignId, baseCTR=0, method="Random")
  data = getCampaignMetricsSimulated(files = c("LinUCB_Disjoint"), campaignId = campaignId, baseCTR=random[1, "CTR"], method="LinUCB_Disjoint", alpha = 0.001) 
  #data = subset(data, RecommendationPart != 0.2)
  data$RecommendationPartGainsRatio = data$FullTPR * 100 / data$RecommendationPart
  all = rbind(all, data) 
}

ratioData <- summarySE2(all, measurevar=c("Ratio"), groupvars=c("RecommendationPart"))
fprData <- summarySE2(all, measurevar=c("RecommendationPartGainsRatio"), groupvars=c("RecommendationPart"))

ratioData$RecommendationPart = factor(ratioData$RecommendationPart)
fprData$RecommendationPart = factor(fprData$RecommendationPart)
g1 = getBarPlot(ratioData, yLabel = "CTR Ratio", title="")

g2 = getBarPlot(fprData, yLabel = "TPR Ratio", title="")

ratioData$RecommendationPart


g = plotGroupNoTitleNoLegend(g1, g2, 9) 
ggsave(paste(imageLocation, "/SimulatedRecommendationSize.png", sep=""), plot=g, width = 20, height = 9, units = "cm")
g
```

```{r Poly_Sigmoid, include=TRUE, echo=FALSE , fig.width = 4}
algorith_name<-"Poly_Sigmoid"
data <- read.csv(file=paste0(path, paste0(algorith_name, ".csv")), header=TRUE, sep=",")
head(data)
data$RowNumber = as.numeric(rownames(data)) %% 133
data$Percent = data$ClickCount / data$Impressions * 100
data$Algorithm = paste(data$OverallCTR)
data_non_random = data[data$AlgoName == "SEGreedy",]


groupedData <- summarySE(data_non_random, 
            measurevar=c("Percent"),
            groupvars=c("Impressions", "AlgoName","OverallCTR", "Algorithm"))

p = ggplot(groupedData, aes(Impressions, y=mean, colour=Algorithm)) + 
  geom_ribbon(aes(ymin=mean-se, ymax=mean+se, linetype=NA, fill=Algorithm), alpha=.3) +
  expand_limits(y=c(0,100)) +
  geom_line() + xlab("Time") + ylab("% of Clicks") +
 theme_bw() + ggtitle("CTR: 0.5%")+ theme(legend.position="bottom",legend.direction="horizontal")

p


#ggsave(paste(imageLocation,"SyntheticCTRComparison.png", sep=""), plot=p4, width = 20, height = 10, units = "cm")

```



```{r Best, include=TRUE, echo=FALSE, warning=FALSE}

files =  c("LinUCB_Disjoint", "Regression", "TS_Lin", "GP_Clustered", "NN", "Random")

path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/837817/Simulated/"

data = prepData(files, path)
data = subset(data, Impressions > 1000 & RecommendationPart == 0.2 & TotalImpressions == max(data$TotalImpressions) )

data = subset(data, (Method == "GP_Clustered" & EqClicks == 0 & ClusterCount == 10 & Hours == 12 & LengthScale == 100 & Nu == 2.5 ) |
                (Method == "NN" & EqClicks == 0.2 & LearningRate == 0.01 ) |
                (Method == "Regression" & EqClicks == 0 & Alpha == 0.001) |
                (Method == "LinUCB_Disjoint" & EqClicks == 0 & Alpha == 0.001)|
                (Method == "TS_Lin" & EqClicks == 0 & Alpha == 0.001)|
                (Method == "Random" ) 
                )
data$Factor = factor(data$Method)

levels(data$Factor) <- c("LinUCB (Disjoint)", "EGreedy (Lin)", "TS (Lin)","GP (Clustered)","NN", "Baseline")

randomClicks = mean(data[data$Method == "Random", "Clicks"])
data$RelativeCTR = data$Clicks/randomClicks

g1 = ggplot(data[data$SimulationId == 2,], aes(x=Factor, y=RelativeCTR, fill=Factor)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_hline(yintercept = 1) +
    ylab("CTR Ratio") + 
    theme_bw() +
    ggtitle("Linear /w Error") +
    scale_y_continuous() +
    labs(fill = "Algorithms:")+
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.title=element_text(size=12), 
        legend.text=element_text(size=10), 
        legend.key.size = unit(1,"line"),
        legend.position="bottom",
        axis.title.y = element_text(size=10)) 
  
g2 = ggplot(data[data$SimulationId == 4,], aes(x=Factor, y=RelativeCTR, fill=Factor)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_hline(yintercept = 1) +
    ylab("CTR Ratio") + 
    ggtitle("Non-Linear /w Error") +
    theme_bw() +
    scale_y_continuous()+
    labs(fill = "Algorithms:")+
    theme( axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position="bottom",
        legend.direction = "horizontal",
        legend.title=element_text(size=12), 
        legend.text=element_text(size=10), 
        axis.title.y = element_text(size=10)) 
p = plotGroupNoTitle(g1, g2, 9) 
p

ggsave(paste(imageLocation, "SimulationCTRRatioComparison_Legend.png", sep=""), plot=p, width = 20, height = 10, units = "cm")
```


```{r CTRMultiplier, include=TRUE, echo=FALSE , fig.width = 4}

path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/837817/Simulated/"
files = c("Random_2", "LinUCB_Disjoint_2")
#files = c("LinUCB_Disjoint_2")
data = prepData(files, path)
data = subset(data, SimulationId == 2 & CTRMultiplier > 0.1)
data$Factor = factor(data$CTRMultiplier)
#data = subset(data, CTRMultiplier < 4)
#getCTRPlot(data, c(0,1), "")
#g1 = getCTRPlot(data, c(0,1), "")
#g2 = getMSEPlot(data, c(0,1), "")
#plotGroup(g1, g2, "Random")

data = subset(data, TotalImpressions == max(data$TotalImpressions))
data$CTR = data$Clicks / data$Impressions
baseline = subset(data, Method == "Random")
data = subset(data, Method != "Random")
data = summarySE2(data, measurevar=c("CTR"), groupvars=c("Factor"))

data$RelativeCTR = data$mean/baseline$CTR 

p = ggplot(data, aes(x=Factor, y=RelativeCTR, fill=Factor)) + 
    geom_bar(position=position_dodge(), stat="identity") +
   # geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
   # geom_hline(yintercept = 1) +
    ylab("CTR Ratio") + 
    theme_bw() +
    scale_y_continuous()+
   xlab("Baseline CTR Multiplier")+
   theme(legend.position="none",   
        plot.title = element_text(size = 14, face = "bold"), 
        axis.title.y = element_text(size=10)) 
   
ggsave(paste(imageLocation,"SimulationCTREffect.png", sep=""), plot=p, width = 7, height = 7, units = "cm")
p
```

















