---
title: "Target Multi-Campaign Simulation Analysis"
output: pdf_document
---


```{r include=TRUE, echo=FALSE,warning=FALSE}
library(ggplot2)
library(gridExtra)
source("~/Documents/ETH/ASL/ASL_Middleware/analysis/R/External.R")
source("~/Documents/ETH/Thesis/1plusX/Data/thesis/R/ManageCampaignsLib.R")
ctrScale = 1.57
imageLocation = "~/Documents/ETH/Thesis/1plusX/Data/thesis/1plusx/Results/Images/Multi-Campaign/"
```

Comparison between real data and simulated data with added clickers. The clickers have behavior based altered by chi distribution with parametrised degrees of freedom and multiplication factor. 
Final formula for an user click/no click is: $ Normal(prediction, stdev) + multiplier * Chi(df) * CTR + Uniform(-0.1, 0.1) * CTR $ 

```{r include=TRUE, echo=FALSE, warning=FALSE}

path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/5/"
simulation_path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/5/Simulation/"

simulated_data = prepData(c("LinUCB_Disjoint_Multi_Target_Chi"), simulation_path)
simulated_data = subset(simulated_data, (ChiDF == 1 & ChiAlpha == 1) | 
                                        (ChiDF == 1 & ChiAlpha == 4) | 
                                        (ChiDF == 10 & ChiAlpha == 4) |
                                        (ChiDF == 100 & ChiAlpha == 1) |
                                        (ChiDF == 100 & ChiAlpha == 4))
simulated_data$Name
simulated_data$Name = paste("DF:", simulated_data$ChiDF, " M:", simulated_data$ChiAlpha, sep="") 

real_data = prepData(c("LinUCB_Disjoint_Multi_Target_Full"), path)
real_data = subset(real_data, (Method == "LinUCB_Disjoint_Multi_Target_Full" & EarlyUpdate == "True" & TargetPercent == 1 & NormalizeTargetValue == "True") ) 
real_data$Name = "Real Data"

data = rbind(simulated_data[c("Name", "Percent", "TotalImpressions", "BatchCTR")], 
             real_data[c("Name", "Percent", "TotalImpressions", "BatchCTR")])

#data = simulated_data[,c("Name", "Percent", "TotalImpressions", "BatchCTR")]
data$Factor = factor(data$Name)
data$TotalImpressions = data$TotalImpressions / max(data$TotalImpressions)
data$Percent = data$Percent * ctrScale

g1 = getCTRPlot(data, c(0,0.3)) + 
  ggtitle("CTR Comparison")

g2 = getClickersPlot(includeRealData = TRUE) 

p = plotGroupNoTitle(g1, g2, 9) 
ggsave(paste(imageLocation, "ChiHindsight.png", sep=""), plot=p, width = 18, height = 10, units = "cm")
p

```

Comparison between Real data, Simulated Hindsight without added clickers and Simulated Lower bound without added clickers. 
For Hindsight click is determined using - $Normal(prediction, stdev) + Uniform(-0.1, 0.1) * CTR$ 
For Lower simulation click either real data click is used or one is generated based on the CTR of the campaign which is chosen.

```{r include=TRUE, echo=FALSE, warning=FALSE}

path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/5/Simulation/"
files =  c("LinUCB_Disjoint_Multi_Target_Full", "LinUCB_Disjoint_Multi", "Random_Multi")
simulated_data = prepData(files, path)
simulated_data = subset(simulated_data, (Alpha == 0 | 
  (Alpha == 0.0001 & SimulationType == "Hindsight" & Method == "LinUCB_Disjoint_Multi") |
  (Alpha == 0.1 & SimulationType == "Lower" & Method == "LinUCB_Disjoint_Multi") |
  (Alpha == 0.1 & SimulationType == "Hindsight" & Method == "LinUCB_Disjoint_Multi_Target" & TargetPercent == 0.8) |
  (Alpha == 0.0001 & SimulationType == "Lower" & Method == "LinUCB_Disjoint_Multi_Target"  & TargetPercent == 0.8)
)) 

simulated_data$Factor = ""
simulated_data[simulated_data$Alpha == 0.0001 & simulated_data$SimulationType == "Hindsight" & simulated_data$Method == "LinUCB_Disjoint_Multi", "Factor"] = "LinUCB Hindsight"

simulated_data[simulated_data$Alpha == 0.1 & simulated_data$SimulationType == "Lower" & simulated_data$Method == "LinUCB_Disjoint_Multi", "Factor"] = "LinUCB Lower"

simulated_data[simulated_data$Alpha == 0.0001 & simulated_data$SimulationType == "Lower" & simulated_data$Method == "LinUCB_Disjoint_Multi_Target", "Factor"] = "LinUCB Lower Target (80%)"

simulated_data[simulated_data$SimulationType == "Hindsight" & simulated_data$Method == "LinUCB_Disjoint_Multi_Target", "Factor"] = "LinUCB Hindsight Target (80%)"

simulated_data[simulated_data$SimulationType == "Hindsight" & simulated_data$Method == "Random_Multi", "Factor"] = "Random Hindsight"
simulated_data[simulated_data$SimulationType == "Lower" & simulated_data$Method == "Random_Multi", "Factor"] = "Random Lower"

#simulated_data$Method = paste(simulated_data$Method, simulated_data$SimulationType, simulated_data$Alpha,
 #                             simulated_data$TargetPercent)

simulated_data$Factor = factor(simulated_data$Factor)

#data$Percent = data$BatchCTR * 100
getCTRPlot(simulated_data, c(0,0.3)) + 
  ggtitle("Simulation - Lower and Hindsight Results")+ 
  theme(plot.title = element_text(size=15,hjust = 0.5))

```

```{r include=TRUE, echo=FALSE, warning=FALSE}

path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/5/Simulation/"
files =  c("LinUCB_Disjoint_Multi_Target_Full", "LinUCB_Disjoint_Multi", "Random_Multi")
simulated_data = prepData(files, path)
simulated_data = subset(simulated_data, SimulationType == "Hindsight" &
                        (( Method == "LinUCB_Disjoint_Multi_Target" & Alpha == 0.0001) |
                          (Method == "LinUCB_Disjoint_Multi" & Alpha == 0.0001) |
                          (Method == "Random_Multi")))

simulated_data$Factor = ""
simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi", "Factor"] = "LinUCB"
simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi_Target", "Factor"] = paste("LinUCB Target (", simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi_Target", "TargetPercent"] * 100, "%)", sep="")
simulated_data[simulated_data$Method == "Random_Multi", "Factor"] = "Random"

simulated_data$Factor = factor(simulated_data$Factor)
#simulated_data$Percent = simulated_data$BatchCTR * 100
getCTRPlot(simulated_data, c(0,0.12)) + 
  ggtitle("Hindsight Simulation Results ")+ 
  theme(plot.title = element_text(size=15,hjust = 0.5))
```

```{r include=TRUE, echo=FALSE, warning=FALSE}

path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/5/Simulation/"
files =  c("LinUCB_Disjoint_Multi_Target_Full", "LinUCB_Disjoint_Multi", "Random_Multi")
simulated_data = prepData(files, path)
simulated_data = subset(simulated_data, SimulationType == "Lower" &
                        (( Method == "LinUCB_Disjoint_Multi_Target" & Alpha == 0.0001) |
                           Method != "LinUCB_Disjoint_Multi_Target"))

simulated_data$Factor = ""
simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi", "Factor"] = "LinUCB"
simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi_Target", "Factor"] = paste("LinUCB Target (", simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi_Target", "TargetPercent"] * 100, "%)", sep="")

simulated_data[simulated_data$Method == "Random_Multi", "Factor"] = "Random"

simulated_data$Factor = factor(simulated_data$Factor)
#simulated_data$Percent = simulated_data$BatchCTR * 100
getCTRPlot(simulated_data, c(0.09,0.12)) + 
  ggtitle("Lower Simulation Results ") + 
  theme(plot.title = element_text(size=15,hjust = 0.5))
```
```{r include=TRUE, echo=FALSE, warning=FALSE}

path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/5/Simulation/"
files =  c("LinUCB_Disjoint_Multi_Target_Full", "LinUCB_Disjoint_Multi", "Random_Multi")
simulated_data = prepData(files, path)

simulated_data = subset(simulated_data, SimulationType == "Hindsight" &
                        (( Method == "LinUCB_Disjoint_Multi_Target" & Alpha == 0.0001) |
                          (Method == "LinUCB_Disjoint_Multi" & Alpha == 0.0001) |
                          (Method == "Random_Multi")))

simulated_data$Factor = ""
simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi", "Factor"] = "No Target"
simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi_Target", "Factor"] = 
  paste("Target ", simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi_Target", "TargetPercent"] * 100, "%", sep="")
simulated_data[simulated_data$Method == "Random_Multi", "Factor"] = "Random"


randomClicks = mean(simulated_data[simulated_data$Factor == "Random", "Clicks"])
no_random = subset(simulated_data, TotalImpressions == max(simulated_data$TotalImpressions) & Factor != "Random")
no_random$RelativeCTR = no_random$Clicks/randomClicks
no_random$Factor = factor(no_random$Factor)
no_random$Factor = factor(no_random$Factor,levels(no_random$Factor)[c(1, 3, 4, 2)])

g1 = ggplot(no_random, aes(x=Factor, y=RelativeCTR, fill=Factor)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_hline(yintercept = 1) +
    ylab("CTR Ratio") + 
    theme_bw() +
    ggtitle("Hindsight") +
    scale_y_continuous() +
    labs(fill = "Algorithms:")+
    theme(axis.title.x=element_blank(),
        legend.position="none",
        axis.title.y = element_text(size=10)) 

files =  c("LinUCB_Disjoint_Multi_Target_Full", "LinUCB_Disjoint_Multi", "Random_Multi")
simulated_data = prepData(files, path)
simulated_data = subset(simulated_data, SimulationType == "Lower" &
                        (( Method == "LinUCB_Disjoint_Multi_Target" & Alpha == 0.0001) |
                           Method != "LinUCB_Disjoint_Multi_Target"))

simulated_data$Factor = ""
simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi", "Factor"] = "LinUCB"
simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi_Target", "Factor"] = paste("LinUCB Target (", simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi_Target", "TargetPercent"] * 100, "%)", sep="")

simulated_data[simulated_data$Method == "Random_Multi", "Factor"] = "Random"
randomClicks = mean(simulated_data[simulated_data$Factor == "Random", "Clicks"])
no_random = subset(simulated_data, TotalImpressions == max(simulated_data$TotalImpressions) & Factor != "Random")
no_random$RelativeCTR = no_random$Clicks/randomClicks
no_random$Factor = factor(no_random$Factor)
no_random$Factor = factor(no_random$Factor,levels(no_random$Factor)[c(1, 3, 4, 2)])
g2 = ggplot(no_random, aes(x=Factor, y=RelativeCTR, fill=Factor)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_hline(yintercept = 1) +
    ylab("CTR Ratio") + 
    theme_bw() +
    ggtitle("Hindsight") +
    scale_y_continuous() +
    labs(fill = "Algorithms:")+
    theme(axis.title.x=element_blank(),
        legend.position="none",
        axis.title.y = element_text(size=10))

#simulated_data$Factor = factor(simulated_data$Factor)
p = plotGroupNoTitle(g1, g2, 9) 
p

```






```{r include=TRUE, echo=FALSE, warning=FALSE}

path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/5/Simulation/"
files =  c("LinUCB_Disjoint_Multi_Target_Full", "LinUCB_Disjoint_Multi", "Random_Multi")
simulated_data = prepData(files, path)

simulated_data = subset(simulated_data, 
                        (( Method == "LinUCB_Disjoint_Multi_Target" & Alpha == 0.0001) |
                           Method != "LinUCB_Disjoint_Multi_Target"))

simulated_data$Factor = ""
simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi", "Factor"] = "No Budgets"
simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi_Target", "Factor"] = 
  paste(simulated_data[simulated_data$Method == "LinUCB_Disjoint_Multi_Target", "TargetPercent"] * 100, "% Budget", sep="")
simulated_data[simulated_data$Method == "Random_Multi", "Factor"] = "Random"

hindsight = subset(simulated_data, SimulationType == "Hindsight")
randomClicks = mean(hindsight[hindsight$Factor == "Random", "Clicks"])
no_random = subset(hindsight, TotalImpressions == max(hindsight$TotalImpressions) & Factor != "Random")
no_random$RelativeCTR = no_random$Clicks/randomClicks
no_random$Factor = factor(no_random$Factor)
no_random$Factor = factor(no_random$Factor,levels(no_random$Factor)[c(4, 2, 3, 1)])

g1 = ggplot(no_random, aes(x=Factor, y=RelativeCTR, fill=Factor)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_hline(yintercept = 1) +
    ylab("CTR Ratio") + 
    theme_bw() +
    expand_limits(y=c(0,4)) + 
    ggtitle("Upper Bound") +
    scale_y_continuous() +
    labs(fill = "Algorithms:")+
    theme(axis.title.x=element_blank(),
        legend.position="none",
        axis.title.y = element_text(size=10),
        axis.text.x = element_text(size=8)) 

lower = subset(simulated_data, SimulationType == "Lower")
randomClicks = mean(lower[lower$Factor == "Random", "Clicks"])
l = subset(lower, TotalImpressions == max(lower$TotalImpressions) & Factor != "Random")
l$RelativeCTR = l$Clicks/randomClicks
l$Factor = factor(l$Factor)
l$Factor = factor(l$Factor,levels(l$Factor)[c(4, 2, 3, 1)])

g2 = ggplot(l, aes(x=Factor, y=RelativeCTR, fill=Factor)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_hline(yintercept = 1) +
    ylab("CTR Ratio") + 
    theme_bw() +
  expand_limits(y=c(0,4)) +
    ggtitle("Lower Bound") +
    scale_y_continuous() +
    labs(fill = "Algorithms:")+
    theme(axis.title.x=element_blank(),
        legend.position="none",
        axis.title.y = element_text(size=10),
        axis.text.x = element_text(size=8))

p = plotGroupNoTitleNoLegend(g1, g2, 9) 

ggsave(paste(imageLocation, "SimulationTargetEffect.png", sep=""), plot=p, width = 18, height = 10, units = "cm")
p

```

```{r include=TRUE, echo=FALSE, warning=FALSE}

path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/5/Simulation/"
files =  c("LinUCB_Disjoint_Multi_Target_All")

simulated_data = prepData(files, path)
simulated_data = subset(simulated_data, SimulationType == "Hindsight" 
                        & SimulationIndex %in% c(1,2,3,5)
                        & (ChiAlpha == 4 | ChiAlpha == 0))

files =  c("LinUCB_Disjoint_Multi_Target_Chi")

#simulated_data2 = prepData(files, path)
#simulated_data2 = subset(simulated_data2, SimulationType == "Hindsight" & SimulationIndex == 5 & ChiAlpha == 4&
    #                       ChiDF == 1)
#simulated_data2$Factor = "Linear /w Chi /w Error Targeted"

simulated_data$Factor = ""
simulated_data[simulated_data$SimulationIndex == 1, "Factor"] = "Linear"
simulated_data[simulated_data$SimulationIndex == 2, "Factor"] = "Linear /w Error"
simulated_data[simulated_data$SimulationIndex == 3, "Factor"] = "Non-Linear /w Error"
simulated_data[simulated_data$SimulationIndex == 5 & simulated_data$ChiAlpha == 4, "Factor"] = "Linear /w Chi /w Error"

simulated_data[simulated_data$Method == "Random_Multi", "Factor"] = "Random"

path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/5/"
real_data = prepData(c("LinUCB_Disjoint_Multi_7days"), path)
real_data = subset(real_data, (Method == "LinUCB_Disjoint_Multi" ) ) 
real_data$Factor = "Real Data"


all = rbind(simulated_data[c("Factor", "Percent", "TotalImpressions", "BatchCTR", "SimulationIndex")], 
             real_data[c("Factor", "Percent", "TotalImpressions", "BatchCTR", "SimulationIndex")])
            #,simulated_data2[c("Factor", "Percent", "TotalImpressions", "BatchCTR", "SimulationIndex")])

all$Factor = factor(all$Factor)
all$Factor = factor(all$Factor,levels(all$Factor)[c(1, 3, 4, 2, 5)])
all$TotalImpressions = all$TotalImpressions / max(all$TotalImpressions)
all$Percent = all$Percent * ctrScale
library(gridExtra)
p = getCTRPlot(all, c(0,0.5), "Simulation Type:", "bottom")+
    theme(legend.justification = c(1, 0), 
          legend.position = c(1, 0),  
          legend.title = element_text(size=10),
          legend.text = element_text(size=8),
          legend.key.height=unit(0.8,"line"),
          legend.box.background = element_rect(colour = "black"))
p

ggsave(paste(imageLocation, "SimulationComparison.png", sep=""), plot=p, width = 9, height = 10, units = "cm")
```




```{r include=TRUE, echo=FALSE, warning=FALSE}

path = "~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/5/Simulation/"
files =  c("LinUCB_Disjoint_Multi_Target_All")

simulated_data = prepData(files, path)
simulated_data = subset(simulated_data, SimulationIndex == 5 & ChiAlpha %in% c(4) & ChiDF == 1)
simulated_data$Factor = "LinUCB"

files =  c("LinUCB_Disjoint_Multi_Target_Chi")

simulated_data2 = prepData(files, path)
simulated_data2 = subset(simulated_data2, SimulationIndex == 5 & ChiAlpha %in% c(4) & ChiDF == 1)
simulated_data2$Factor = "T_LinUCB"

simulated_data[simulated_data$Method == "Random_Multi", "Factor"] = "Random"

all = rbind(simulated_data[c("Factor", "Percent", "TotalImpressions", "BatchCTR", "SimulationIndex")], 
             simulated_data2[c("Factor", "Percent", "TotalImpressions", "BatchCTR", "SimulationIndex")])

all$Factor = factor(all$Factor)
all$Factor = factor(all$Factor, levels(all$Factor)[c(3, 1, 4, 2)])
all$TotalImpressions = all$TotalImpressions / max(all$TotalImpressions)
all$Percent = all$Percent * ctrScale

#all = subset(all, TotalImpressions == max(all$TotalImpressions))

p2 = getCTRPlot(all, c(0,0.5), "Simulation Type:", "right") + 
  scale_color_brewer(palette="Paired", name="Algorithm:")+
  theme(legend.justification = c(1, 0), 
          legend.position = c(1, 0),  
        legend.title = element_text(size=10),
        legend.text = element_text(size=8),
          legend.key.height=unit(0.8,"line"),
          legend.box.background = element_rect(color = "black"))
p2

ggsave(paste(imageLocation, "SimulationAlgoComparison.png", sep=""), plot=p2, width = 9, height = 10, units = "cm")


```
















