---
title: "1PlusX - Campaign 837817"
author: "Ana Dimitrova"
output: pdf_document
geometry: margin=1cm
---
 

```{r setup, include=TRUE, echo=FALSE,warning=FALSE}
library(ggplot2)
library(scales)
library(gridExtra)

campaign_id = 866128
imageLocation = "~/Documents/ETH/Thesis/1plusX/Data/thesis/1plusx/Results/Images/Single-Campaign/"
path = paste("~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/", campaign_id, "/", sep="")
path_ctr = paste("~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/CTR/", campaign_id, "/", sep="")

formatterM <- function(){
  function(x) paste(x/1000000, "M")
}
formatterPercent <- function(){
  function(x) paste(x, "%")
}
selectNecessaryColumns <- function(df, columns) {
  for (column in columns) {
    if(!(column %in% colnames(df))){
      df[column] = NA
    } 
  }
  df[,columns]
}

```


\section*{\centering {Best performance per algorithm for 20\% recommendation size}}
```{r Best, include=TRUE, echo=FALSE, warning=FALSE}
source("~/Documents/ETH/ASL/ASL_Middleware/analysis/R/External.R")

# 597165 - 0.001
# 722100 - 0.01, 0.001
# 809153 - to rerun entirely
columnNames = c("CampaignId", "Method", "RecommendationPart", "CTR", "Clicks", "Impressions", "FullFNR", "FullTPR", "BaseCTR", "Ratio")
all = data.frame(matrix(vector(), 0, length(columnNames), dimnames=list(c(), columnNames)), stringsAsFactors=F)
campaignIds = c(597165, 837817, 722100, 809153)
files =  c("Random")
for (campaignId in campaignIds)
{
  random = getCampaignMetrics(files =  c("Random"),  campaignId = campaignId, baseCTR=0, method="Random")
  data = getCampaignMetrics(files = c("LinUCB_Disjoint_Metrics"), campaignId = campaignId, baseCTR=random[1, "CTR"], method="LinUCB_Disjoint", alpha = 0.01) 
  data$RecommendationPartGainsRatio = data$FullTPR * 100 / data$RecommendationPart
  all = rbind(all, data) 
}
data$RecommendationPart = factor(data$RecommendationPart)
ratioData <- summarySE2(all, measurevar=c("Ratio"), groupvars=c("RecommendationPart"))
fprData <- summarySE2(all, measurevar=c("RecommendationPartGainsRatio"), groupvars=c("RecommendationPart"))
ratioData$RecommendationPart = factor(ratioData$RecommendationPart)
fprData$RecommendationPart = factor(fprData$RecommendationPart)
g1 = getBarPlot(ratioData, yLabel = "CTR Ratio", title="")
g2 = getBarPlot(fprData, yLabel = "TPR Ratio", title="")

g = plotGroupNoTitleNoLegend(g1, g2, 9) 
ggsave(paste(imageLocation, "RecommendationSize.png"), plot=g, width = 18, height = 9, units = "cm")
g
```

```{r Best, include=TRUE, echo=FALSE, warning=FALSE}

#files = c("Regression_Test")
files =  c("GP_Clustered_Metrics", "NN_Metrics", "LinUCB_Disjoint_Metrics", "Regression_Metrics", "Random_Metrics","TS_Lin_Metrics")
#files =  c("LinUCB_Disjoint_Metrics", "Random_Metrics")
campaign_id = 837817
ctrScale = 1.57
path = paste("~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/", campaign_id, "/", sep="")

data = prepData(files, path)

#files = c("Regression_Test")

data = subset(data, Impressions > 1000 & RecommendationPart == 0.2 )
data$TotalImpressions = data$TotalImpressions / max(data$TotalImpressions)

data = subset(data, (Method == "GP_Clustered" & EqClicks == 0 & ClusterCount == 10 & Hours == 12 & LengthScale == 100 & Nu == 2.5 ) |
                (Method == "NN" & EqClicks == 0.2 & LearningRate == 0.001 ) |
                (Method == "Regression" & EqClicks == 0 & Alpha == 0.01) |
                (Method == "LinUCB_Disjoint" & EqClicks == 0 & Alpha == 0.01)|
                (Method == "TS_Lin" & EqClicks == 0 & Alpha == 0.001)|
                (Method == "Baseline" ) 
                )
data$Factor = factor(data$Method)
levels(data$Factor) <- c("GP (Clustered)","NN","LinUCB (Disjoint)", "EGreedy (Lin)", "Baseline", "TS (Lin)")

data$Percent = data$Percent * ctrScale 
g1 = getCTRPlot(data, c(0,0.75), scaleName = "Algorithms")  
g2 = getMSEPlot(data, c(0,0.003), "Algorithms:")

g = plotGroupNoTitle(g1, g2, 9) 
g
ggsave(paste(imageLocation, "AllAlgorithms.png", sep=""), plot=g, width = 18, height = 10, units = "cm")
```
\newpage
\section*{\centering Random}
```{r Random, include=TRUE, echo=FALSE, fig.width = 10, fig.asp = 1}

files =  c("Random")
data = prepData(files)
data$Factor = factor(data$Method)

g1 = getCTRPlot(data, c(0,1), "")
g2 = getMSEPlot(data, c(0,1), "")

plotGroup(g1, g2, "Random")
```
\newpage
\section*{\centering GP CTR and modified MSE}
Recommendation for all of the experiements for GP is 20% size.
```{r GP, include=TRUE, echo=FALSE, fig.width = 10, fig.asp = 1}

files =  c("GP_Clustered")
data = prepData(files)
data = subset(data, Impressions > 1000)

data1 = subset(data, Nu == 2.5 & Hours == 12 & LengthScale == 100 & ClusterCount == 10)
data1$Factor = factor(paste(data1$EqClicks, sep = ""))

data2 = subset(data, EqClicks == 0 & Hours == 12 & LengthScale == 100 & ClusterCount == 10)
data2$Factor = factor(paste(data2$Nu, sep = ""))

data3 = subset(data, EqClicks == 0 & Hours == 12 & LengthScale == 100 & Nu == 2.5)
data3$Factor = factor(paste(data3$ClusterCount , sep = ""))

g1 = getCTRPlot(data1, c(0,1), "EQ:")+ ggtitle("EQ - Nu:2.5,H:12,CC:10")
g2 = getCTRPlot(data2, c(0,1), "Nu:")  + ggtitle("Nu - EQ:0,H:12,CC:10")
g3 = getCTRPlot(data3, c(0,1), "CC:")   + ggtitle("CC - EQ:0.2,Nu:2.5,H:12")
grid.arrange(g1, g2, g3, nrow=1, ncol=3, widths=unit(c(6.2, 6.2, 6.2), "cm"), heights=unit(8, "cm"), top="GP results")

```
\break\break
```{r GP_MSE, include=TRUE, echo=FALSE, fig.width = 10, fig.asp = 1}

files =  c("GP_Clustered")
data = prepData(files)
data = subset(data, Impressions > 1000)

data1 = subset(data, Nu == 2.5 & Hours == 12 & LengthScale == 100 & ClusterCount == 10)
data1$Factor = factor(paste(data1$EqClicks, sep = ""))

data2 = subset(data, EqClicks == 0 & Hours == 12 & LengthScale == 100 & ClusterCount == 10)
data2$Factor = factor(paste(data2$Nu, sep = ""))

data3 = subset(data, EqClicks == 0.2 & Hours == 12 & LengthScale == 100 & Nu == 2.5)
data3$Factor = factor(paste(data3$ClusterCount , sep = ""))

g1 = getMSEPlot(data1, c(0,0.01), "EQ:")+ ggtitle("EQ - Nu:2.5,H:12,CC:10")
g2 = getMSEPlot(data2, c(0,0.01), "Nu:")  + ggtitle("Nu - EQ:0,H:12,CC:10")
g3 = getMSEPlot(data3, c(0,0.01), "CC:")   + ggtitle("CC - EQ:0.2,Nu:2.5,H:12")
grid.arrange(g1, g2, g3, nrow=1, ncol=3, widths=unit(c(6.2, 6.2, 6.2), "cm"), heights=unit(8, "cm"), top="GP MMSE results")

```


\newpage
\section*{\centering LinUCB CTR and modified MSE}
```{r LinUCB, include=TRUE, echo=FALSE, fig.width = 10, fig.asp = 1}

files =  c("LinUCB_Disjoint")
data = prepData(files)
data = subset(data, Impressions > 1000)

data_alpha = subset(data, EqClicks == 0.0 & RecommendationPart == 0.02)
data_alpha$Factor = factor(paste(data_alpha$Alpha, sep = ""))

data_rec = subset(data, Alpha == 0.1 & EqClicks == 0.0)
data_rec$Factor = factor(paste(data_rec$RecommendationPart * 100, "%",sep = ""))

data_eq = subset(data, RecommendationPart == 0.02 & Alpha == 0.1)
data_eq$Factor = factor(paste(data_eq$EqClicks*100, "%", sep = ""))

g1 = getCTRPlot(data_alpha, c(0,3), "Alpha:")  + ggtitle("Alpha Change-EQ:0,Rec:0.2")
g2 = getCTRPlot(data_rec, c(0,1), "Rec:")      + ggtitle("Rec. Change-Alpha:0.1")
g3 = getCTRPlot(data_eq, c(0,1), "EQ:")        + ggtitle("EQ Change-Alpha:0.1")
grid.arrange(g1, g2, g3, nrow=1, ncol=3, widths=unit(c(6.2, 6.2, 6.2), "cm"), heights=unit(8, "cm"), top="LinUCB results")

```
\break\break
```{r LinUCB_MSE, include=TRUE, echo=FALSE, fig.width = 10, fig.asp = 1}

files =  c("LinUCB_Disjoint")
data = prepData(files)
data = subset(data, Impressions > 1000)

data_alpha = subset(data, EqClicks == 0.0 & RecommendationPart == 0.02)
data_alpha$Factor = factor(paste(data_alpha$Alpha, sep = ""))

data_rec = subset(data, Alpha == 0.1 & EqClicks == 0.0)
data_rec$Factor = factor(paste(data_rec$RecommendationPart * 100, "%",sep = ""))

data_eq = subset(data, RecommendationPart == 0.02 & Alpha == 0.1)
data_eq$Factor = factor(paste(data_eq$EqClicks*100, "%", sep = ""))

g1 = getMSEPlot(data_alpha, c(0,0.001), "Alpha:")  + ggtitle("Alpha Change-EQ:0,Rec:0.2")
g2 = getMSEPlot(data_rec, c(0,0.001), "Rec:")      + ggtitle("Rec. Change-Alpha:0.1")
g3 = getMSEPlot(data_eq, c(0,0.001), "EQ:")        + ggtitle("EQ Change-Alpha:0.1")
grid.arrange(g1, g2, g3, nrow=1, ncol=3, widths=unit(c(6.2, 6.2, 6.2), "cm"), heights=unit(8, "cm"), top="LinUCB MMSE results")

```

\newpage
\section*{\centering Regression CTR and modified MSE}
```{r Regression, include=TRUE, echo=FALSE, fig.width = 10, fig.asp = 1}

files =  c("Regression")
data = prepData(files)
data = subset(data, Impressions > 1000)

data_alpha = subset(data, EqClicks == 0.0 & RecommendationPart == 0.02)
data_alpha$Factor = factor(paste(data_alpha$Alpha, sep = ""))

data_rec = subset(data, Alpha == 0.1 & EqClicks == 0.0)
data_rec$Factor = factor(paste(data_rec$RecommendationPart * 100, "%",sep = ""))

data_eq = subset(data, RecommendationPart == 0.02 & Alpha == 0.1)
data_eq$Factor = factor(paste(data_eq$EqClicks*100, "%", sep = ""))

g1 = getCTRPlot(data_alpha, c(0,3), "Alpha:")  + ggtitle("Alpha Change-EQ:0,Rec:0.2")
g2 = getCTRPlot(data_rec, c(0,1), "Rec:")      + ggtitle("Rec. Change-Alpha:0.1")
g3 = getCTRPlot(data_eq, c(0,1), "EQ:")        + ggtitle("EQ Change-Alpha:0.1")
grid.arrange(g1, g2, g3, nrow=1, ncol=3, widths=unit(c(6.2, 6.2, 6.2), "cm"), heights=unit(8, "cm"), top="Regression results")

```
\break\break
```{r Regression_MSE, include=TRUE, echo=FALSE, fig.width = 10, fig.asp = 1}

files =  c("Regression")
data = prepData(files)
data = subset(data, Impressions > 1000)

data_alpha = subset(data, EqClicks == 0.0 & RecommendationPart == 0.02)
data_alpha$Factor = factor(paste(data_alpha$Alpha, sep = ""))

data_rec = subset(data, Alpha == 0.1 & EqClicks == 0.0)
data_rec$Factor = factor(paste(data_rec$RecommendationPart * 100, "%",sep = ""))

data_eq = subset(data, RecommendationPart == 0.02 & Alpha == 0.1)
data_eq$Factor = factor(paste(data_eq$EqClicks*100, "%", sep = ""))

g1 = getMSEPlot(data_alpha, c(0,0.001), "Alpha:")  + ggtitle("Alpha Change-EQ:0,Rec:0.2")
g2 = getMSEPlot(data_rec, c(0,0.001), "Rec:")      + ggtitle("Rec. Change-Alpha:0.1")
g3 = getMSEPlot(data_eq, c(0,0.001), "EQ:")        + ggtitle("EQ Change-Alpha:0.1")
grid.arrange(g1, g2, g3, nrow=1, ncol=3, widths=unit(c(6.2, 6.2, 6.2), "cm"), heights=unit(8, "cm"), top="Regression MMSE results")

```

\newpage
\section*{\centering NN CTR and modified MSE}
```{r NN, include=TRUE, echo=FALSE}
#, fig.width = 10, fig.asp = 1
files =  c("NN_Metrics")
data = prepData(files)
data = subset(data, Impressions > 1000)

data1 = subset(data, EqClicks == 0.2 & LearningRate == 0.01)
data1$Factor = factor(paste(data1$RecommendationPart * 100, "%", sep = ""))

data2 = subset(data, EqClicks == 0.2 & RecommendationPart == 0.2)
data2$Factor = factor(paste(data2$LearningRate, sep = ""))

data3 = subset(data, EqClicks == 0.5 & RecommendationPart == 0.2)
data3$Factor = factor(paste(data3$LearningRate, sep = ""))

g1 = getCTRPlot(data1, c(0,1), "Rec:")  + ggtitle("Rec Change-EQ:0.2")
g2 = getCTRPlot(data2, c(0,1), "LRate:")+ ggtitle("LRate Change")
g3 = getCTRPlot(data3, c(0,1), "LRate:")+ ggtitle("LRate Change-EQ:0.2")
grid.arrange(g1, g2, g3, nrow=1, ncol=3, widths=unit(c(6.2, 6.2, 6.2), "cm"), heights=unit(8, "cm"), top="NN results")

```
\newpage
\section*{\centering TS Lin CTR and modified MSE}
```{r TS_Lin, include=TRUE, echo=FALSE, fig.width = 10, fig.asp = 1}

files =  c("TS_Lin")
data = prepData(files)
data = subset(data, Impressions > 1000)

data_alpha = subset(data, EqClicks == 0.0 & RecommendationPart == 0.02)
data_alpha$Factor = factor(paste(data_alpha$Alpha, sep = ""))

data_rec = subset(data, Alpha == 0.001 & EqClicks == 0.0)
data_rec$Factor = factor(paste(data_rec$RecommendationPart * 100, "%",sep = ""))

data_eq = subset(data, RecommendationPart == 0.02 & Alpha == 0.001)
data_eq$Factor = factor(paste(data_eq$EqClicks*100, "%", sep = ""))

g1 = getCTRPlot(data_alpha, c(0,3), "Alpha:")  + ggtitle("Alpha Change-EQ:0,Rec:0.2")
g2 = getCTRPlot(data_rec, c(0,3), "Rec:")      + ggtitle("Rec. Change-Alpha:0.001")
g3 = getCTRPlot(data_eq, c(0,3), "EQ:")        + ggtitle("EQ Change-Alpha:0.001")
grid.arrange(g1, g2, g3, nrow=1, ncol=3, widths=unit(c(6.2, 6.2, 6.2), "cm"), heights=unit(8, "cm"), top="TS_Lin results")

```
\break\break
```{r TS_Lin_MSE, include=TRUE, echo=FALSE, fig.width = 10, fig.asp = 1}

files =  c("TS_Lin")
data = prepData(files)
data = subset(data, Impressions > 1000)

data_alpha = subset(data, EqClicks == 0.0 & RecommendationPart == 0.02)
data_alpha$Factor = factor(paste(data_alpha$Alpha, sep = ""))

data_rec = subset(data, Alpha == 0.001 & EqClicks == 0.0)
data_rec$Factor = factor(paste(data_rec$RecommendationPart * 100, "%",sep = ""))

data_eq = subset(data, RecommendationPart == 0.02 & Alpha == 0.001)
data_eq$Factor = factor(paste(data_eq$EqClicks*100, "%", sep = ""))

g1 = getMSEPlot(data_alpha, c(0,0.001), "Alpha:")  + ggtitle("Alpha Change-EQ:0,Rec:0.2")
g2 = getMSEPlot(data_rec, c(0,0.001), "Rec:")      + ggtitle("Rec. Change-Alpha:0.1")
g3 = getMSEPlot(data_eq, c(0,0.001), "EQ:")        + ggtitle("EQ Change-Alpha:0.1")
grid.arrange(g1, g2, g3, nrow=1, ncol=3, widths=unit(c(6.2, 6.2, 6.2), "cm"), heights=unit(8, "cm"), top="TS_Lin MMSE results")

```

```{r all, include=TRUE, echo=FALSE}

files =  c("TS_Lin", "NN", "LinUCB_Disjoint", "Regression", "GP_Clustered")
data = prepData(files)
data$Factor = factor(data$Method)

data = subset(data, Impressions > 1000 & RecommendationPart == 0.2 )
data = subset(data, 
                (Method == "GP_Clustered" & EqClicks == 0 & ClusterCount == 10 & Hours == 12 & LengthScale == 100 & Nu == 2.5 ) |
                (Method == "NN" & EqClicks == 0.5 & LearningRate == 0.01 ) |
                (Method == "Regression" & EqClicks == 0 & Alpha == 0.01) |
                (Method == "LinUCB_Disjoint" & EqClicks == 0 & Alpha == 0.01)|
                (Method == "TS_Lin" & EqClicks == 0 & Alpha == 0.001)|
                (Method == "Random" ) 
                )

ggplot(data, aes(x=Timestamp, y=Impressions, colour=Factor)) + 
    geom_line() +
    xlab("Timestamp") + ylab("Cumulative Common Impressions") +
    scale_y_continuous(labels=formatterM()) +
    theme_bw() +
    ggtitle("Cumulative # Impressions during Exploration Scavanging")
  
``` 

```{r Best, include=TRUE, echo=FALSE, warning=FALSE}

#files = c("Regression_Test")
files =  c("GP_Clustered_Metrics", "NN_Metrics", "LinUCB_Disjoint_Metrics", "Regression_Metrics", "Random_Metrics","TS_Lin_Metrics")
#files =  c("LinUCB_Disjoint_Metrics", "Random_Metrics")
campaign_id = 837817
ctrScale = 1.57
path = paste("~/Documents/ETH/Thesis/1plusX/Data/Thesis/1plusx/Results/", campaign_id, "/", sep="")

data = prepData(files, path)

#files = c("Regression_Test")

data = subset(data, Impressions > 1000 & RecommendationPart == 0.2 )
data$TotalImpressions = data$TotalImpressions / max(data$TotalImpressions)

data = subset(data, (Method == "GP_Clustered" & EqClicks == 0 & ClusterCount == 10 & Hours == 12 & LengthScale == 100 & Nu == 2.5 ) |
                (Method == "NN" & EqClicks == 0.2 & LearningRate == 0.001 ) |
                (Method == "Regression" & EqClicks == 0 & Alpha == 0.01) |
                (Method == "LinUCB_Disjoint" & EqClicks == 0 & Alpha == 0.01)|
                (Method == "TS_Lin" & EqClicks == 0 & Alpha == 0.001)|
                (Method == "Baseline" ) 
                )
data$Factor = factor(data$Method)
levels(data$Factor) <- c("GP (Clustered)","NN","LinUCB (Disjoint)", "EGreedy (Lin)", "Baseline", "TS (Lin)")

data$Percent = data$Percent * ctrScale 


data = data[data$TotalImpressions == max(data$TotalImpressions), ]

data$Relative = data$Percent / data[data$Method == "Baseline", "Percent"]
data[order(data$Percent), c("Method", "Percent","Relative")]
```